---
title: "Testing Functions"
author: "Group2-Jing Lin, Yael Yossefy, Yaqian Han"
format: html
editor: visual
output:
  html_document:
    toc: yes
    toc_depth: 2
    toc_float: yes
    fig_height: 6
    fig_width: 8
---

```{r,echo=FALSE}
knitr::opts_chunk$set(cache=TRUE, error=FALSE, message=FALSE, warning=FALSE,
                      echo=T, tidy.opts=list(width.cutoff=60),tidy=TRUE)

```

## Function 1

Function 1: Write a function that makes a boxplot of payments by DRG code. Make it an option for your function to do this for either the average Medicare payments, the average total payment, or the average covered charges

```{r load libraries}
library(ggplot2)
library(dplyr)
library(lab2group2)
```

```{r load data}
DRG_data <- read.csv("DRG_data.csv")
```


```{r}
# Testing boxplot_function
plot1 <- boxplot_function(DRG_data, "medicare")
print(plot1)

plot2 <- boxplot_function(DRG_data, "total")
print(plot2)

plot3 <- boxplot_function(DRG_data, "covered")
print(plot3)
```

## Function 2

Function 2: Write a function that calculates statistics over all of the DRG codes for average Medicare payments. Make it an option in your function to calculate either the mean, median, or standard deviation of the DRG codes.

```{r}
# Testing mean
mean_payment <- summary_function(DRG_data, "mean")
print("Mean of average Medicare payments by DRG Definition:")
print(mean_payment)

# Testing median
median_payment <- summary_function(DRG_data, "median")
print("Median of average Medicare payments by DRG Definition:")
print(median_payment)

# Testing standard deviation
sd_payment <- summary_function(DRG_data, "sd")
print("Standard deviation of average Medicare payments by DRG Definition:")
print(sd_payment)
```
